### 2016-05-02 text/ms.Rmd
Minor edits to the manuscript

We fit four individual data-limited models that use data on catch and basic
life-history parameters to estimate $B/B_\mathrm{MSY}$. We chose these models
because because they can be fit to the vast majority of fisheries around the
world, are established in the literature, and have been extensively simulation
tested [@rosenberg2014].

@@

Superensemble models allow us to incorporate additional covariates and
potentially leverage interactions between these covariates and individual model
predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical properties
of the data. For simplicity, and since many possible covariates, such as fishing
effort dynamics, would not be known for many real-world data-limited scenarios,
we added only one set of additional covariates: spectral properties of the catch
time series. Spectral analysis decomposes a time series into the frequency
domain and provides a means of describing the cyclical shape of the catch series
that is independent of time series length (except in affecting precision) and
independent of absolute magnitude of catch. We fit spectral models to the
scaled catch time series (catch divided by maximum catch) with the `spec.ar`
function in R and recorded representative short- and long-term spectral
densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year
cycles. We include the results of adding these additional covariates in the
supplementary materials.

@@

Once the superensemble models are built, we can apply them to new stocks that
we'd like to know the status of. To do this we applied the individual models
to our stocks of interest and then applied these data to our already built
superensemble models. In this paper we applied the superensemble models to
subsets of the simulated data as a cross validation test and to the RAM Legacy
Stock Assessment database to test on real stocks.

@@

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database
--- a compilation of stock-assessment output from hundreds of exploited marine
populations around the world. Our analysis of the stock-assessment database was
based on version 2.5. After removing stocks for which at least one of the
individual models described below did not converge (121), this database
included `r ram_stocks_n` stocks. We removed these stocks for all methods ---
both for the individual and superensemble models. An alternative would be to
fit superensemble models to subsets of the individual models that did converge,
but for the purposes of this paper we will only use superensemble models that
use all four individual models.

@@

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. Such individual models would
be expected to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each superensembles? Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate 'real' dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a more general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g. parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.

>>>>

We fit four individual data-limited models that use catch data and basic
life-history parameters to estimate $B/B_\mathrm{MSY}$. We chose these models
because they can be fit to the vast majority of fisheries around the
world, are established in the literature, and have been extensively simulation
tested [@rosenberg2014].

@@

Superensemble models allow us to incorporate additional covariates and
potentially leverage interactions between these covariates and individual model
predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. We tested the performance benefits of including one set
of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the cyclical shape of the catch series that is
independent of time series length (except in affecting precision) and
independent of absolute magnitude of catch. We fit spectral models to the
scaled catch time series (catch divided by maximum catch) with the `spec.ar`
function in R and recorded representative short- and long-term spectral
densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year
cycles. We include the results of adding these additional covariates in the
supplementary materials.

@@

Once the superensemble models are built, we can apply them to new stocks that
we'd like to know the status of. To do this we applied the individual models
to our stocks of interest and then applied these data to our already built
superensemble models. In this paper we applied the superensemble models to
subsets of the simulated data as a cross-validation test and to the RAM Legacy
Stock Assessment database to test on real stocks.

@@

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database
--- a compilation of stock-assessment output from hundreds of exploited marine
populations around the world. Our analysis of the stock-assessment database was
based on version 2.5. After removing stocks for which at least one of the
individual models described below did not converge (121), this database
included `r ram_stocks_n` stocks. We removed these stocks for all methods ---
both for the individual and superensemble models. An alternative would be to
fit superensemble models to subsets of the individual models that did converge,
but for simplicity we will only use superensemble models fitted to all four
individual models.

@@

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. Such individual models would
be expected to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each superensembles. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate 'real' dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in fisheries and ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g. parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.
